---
title: "Day 12 Self-learning"
author: "Jian Li"
date: "1/26/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.width=8,collapse=TRUE)
```

#Part1 R code chunks and inline R code
Besides  code chunks, you can also insert values of R objects inline in text. For example:
```{r}
x = 5 # radius of a circle
```
For a circle with the radius `r x`, its area is `r pi*x^2`

#Part2 Figures
```{r}
plot(cars,pch=18)
```
You can provide a figure caption using fig.cap in the chunk options. If the document output format supports the option fig_caption:true (e.g., the output format rmarkdown::html_document), the R plots will be placed into figure environments. In the case of PDF output, such figures will be automatically numbered. If you aslo want to number figures in other formats (suh as HTML). please see the bookdown package in Chapter 12. 

PDF documents are generated through the LaTex files generated from R Markdown. A highly surprising fact to LaTex beginners is that figures float by default: even if you generate a plot in a code chunk on the first page, the whole figure environment may flaot to the next page. This is just how LaTex works by default. It has a tendency to float figures to the top or bottom of pages. Although it can be annoying and distracing, we recommend that you refrain from playing the "Whac-A-Mole" game in the beginning of your writing, i.e., desparately trying to position figures "correctly" while they seem to be always dodging you. You may wish to fine-tune the positions once the content is complete using the fig.pos chunk option (e.g., fig.pos='h'). 

To place multiple figures side-by-side from the same code chunk, you can use the fig.show='hold' option along with the out.width option. Below is an example with two plots, each with a width of 50%.

```{r,fig.cap="FIGURE 2.5: Two plots side-by-side",fig.align='center'}
par(mar=c(4,4,0.2,0.1),mfrow=c(1,2))
plot(cars,pch=19)
plot(pressure,pch=17)
```

#Tables
The easiest way to include tables is by using knitr::kable(), which can create tables for HTML, PDF and Word outputs. Table captions can be included by passing caption to the function, e.g.,
```{r table-mtcars}
knitr::kable(iris[1:5,],caption='A Caption')
```

#Other language engines
```{python}
x='hello, python world!'
print(x.split(' '))
```

