---
title: "Day5 Self Learning"
author: "Jian Li"
date: "1/19/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Relationship to base and plyr functions




```{r,echo=TRUE}
library(purrr)
library(repurrrsive)
```

lapply() vs. purrr::map()
These are the core mapping functions of base and purrr,respectively. They are "list in,list out". The main(only?) difference is access to purrr's shortcuts for indexing by name or position and for creating anonymous functions.

##What R **base** can do:
```{r,echo=TRUE}
lapply(got_chars[1:3],function(x) x[["name"]])
```

##What **purrr** can do:
```{r,echo=TRUE}
map(got_chars[1:3],"name")
map_dfr(got_chars[23:25],`[`,c("name","playedBy"))

tibble::tibble(
  name=map_chr(got_chars[23:25],"name"),
  id=map_int(got_chars[23:25],"id")
)
```


##mapply() vs. map2(),pmap():
when you need to iterate over 2 ore more vectors/lists in parallel,the base option is mapply(). Unlike the other apply functions, the first arguments is FUN, the function to apply, and the multiple vector inputs are provided "loose" via ....
\newline
For exactly two vector inputs, purrr has map2(), with all the usual tyep-specific variants. For an arbitrary number of vector inputs, use purrr pmap() or type-specific variants, with the inputs packaged in a list. A very handy special case is when the input is a data frame, in which case pmap_*() applies .f to each row.


```{r,echo=TRUE}
nms<- got_chars[16:18] %>% map_chr("name")
birth<- got_chars[16:18] %>% map_chr("born")

df<- tibble::tibble(nms,
                    connector="was born",
                    birth)
pmap_chr(df,paste)
 
```

##aggregate() vs. dplyr::summarise() 
consider a data frame, as opposed to a nested list. How do you split it into pieces, according to one or more factors, apply a function to the pieces, and combine the results?
\newline
Create a tiny excerpt of the Gapminder dataset that contains a bit of data for Canada and Germany. Load dplyr, now that we are more in the data frame world.
```{r,echo=TRUE}
library(dplyr)
library(gapminder)
mini_gap<- gapminder %>% filter(country %in% c("Canada","Germany"),year>2000) %>% droplevels()

mini_gap %>% group_by(country) %>% summarise_at(vars(lifeExp,gdpPercap),mean)
```
##by() vs tidyr::nest()
```{r,echo=TRUE}
by_obj<- by(gapminder,
            gapminder$country,
            function(df) lm(lifeExp~year,data=df))
str(by_obj[1:2],max.level=1)

library(tidyr)
nested_df<- gapminder %>% group_by(country,continent) %>% nest() %>% mutate(fit=map(data,~lm(lifeExp~year,data=.x)))
str(nested_df$fit[1:2],max.level=1)
```

What if you want to inspect the fits for Oceania? On the tidyverse side, where the fits live in a data frame that carriers country and continent info, we can use our usual techniques for filtering rows based on the data.
```{r,echo=TRUE}
nested_df %>% filter(continent=="Oceania") %>% .$fit
```

##Final form a data frame with all info
```{r,echo=TRUE}
nested_df %>% mutate(coefs=map(fit,coef),
                     intercept=map_dbl(coefs,1),
                     slope=map_dbl(coefs,2)) %>%
  select(country,continent,intercept,slope)

```

#Tomorrow to-do list:
Start take a peak at **gganimate** package\    

Click [me](https://gganimate.com)